Data Specialization for a Staged Lambda Calculus

### 2015-02-28 paper/conclusion.tex
Editing pass on conclusion.

This paper presents an algorithm for translating programs written in a
staged lambda calculus into multi-pass programs, which evaluate as two
monostage programs in a sequence of two dependent passes. We present a
formalization of the techniques in a way that can be implemented in
practice.  While we have provided an implementation of this algorithm
that successfully splits the examples considered in this paper, we
have stopped short of offering a full proof of correctness, which we
leave for future work.

In addition, we are interested in providing a more complete system
implementation as well as investigating how ideas from \lang\ and the
its splitting algorithm can be integrated into existing practical
systems such as staged programming systems for computer graphics
pipelines.  On the more conceptual side, it would be interesting to
consider the extension of our splitting techniques to richer source
languages, for example, those that include parallelism.

>>>>

This paper provides a formal presentation of an algorithm for
statically translating programs written in a two-stage lambda calculus
into multi-pass programs, which evaluate as two monostage programs in
two dependent passes.  While we have provided an implementation of
this algorithm that successfully splits the examples considered in
this paper, we have stopped short of offering a full proof of
correctness, which we leave for future work.

In addition, we are interested in exploring the behavior of splitting
for a broader set of examples as well as investigating how ideas from
\lang\ and its splitting algorithm can be integrated into existing
practical systems such as staged programming systems for computer
graphics pipelines.  On the more conceptual side, it would be
interesting to consider the extension of our splitting techniques to
richer source languages that include mutation, parallel constructs,
and more than two stages.
